A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-07-11 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
Replace Wigner example with Husimi Q
The Husimi Q functions give a better example of functions where orthogonality doesn't imply disjoint support.

I added a reference to support our claim.

For example, the eigenstates $| m \rangle$ of the harmonic oscillator are orthogonal, mutually exclusive events. Their corresponding Wigner functions are
\begin{equation}
	W_m (q, p) = \frac{(-1)^m}{\pi} e^{-(q^2+p^2)} L_m (2(q^2 + p^2)).
\end{equation}
Their support is the whole $\mathbb{R}^2$ since the Laguerre polynomials $L_m$ have finitely many zeros, and therefore are not disjoint. Conversely, in a SIC-POVM we take $d^2$ pure states $P_i$ in a $d$ dimensional space, which means they cannot be all orthogonal to each other. For a Bloch sphere, the four corners of the tetrahedron are not all opposite to each other. Therefore, disjoint sets of $P_i$ do not correspond to mutually exclusive events.

>>>>

For example, the Husimi Q functions of pure states $Q_\psi(\alpha) = \frac{1}{\pi} |\langle \alpha | \psi \rangle|^2$ have support everywhere, since we can express the inner product as \cite[eq. 11.7-1]{mandel1995}
\begin{equation}
	\langle \alpha | \psi \rangle = e^{-|\alpha|^2/2} F_\psi(\alpha^\ast)
\end{equation}
where $F_\psi$ is an entire analytic function. Conversely, in a SIC-POVM we take $d^2$ pure states $P_i$ in a $d$ dimensional space, which means they cannot be all orthogonal to each other. For a Bloch sphere, the four corners of the tetrahedron are not all opposite to each other. Therefore, disjoint sets of $P_i$ do not correspond to mutually exclusive events.
